% I can't recall where I found this template or who wrote it.  But,
% its excellent.  Kudos to whomever put it together.

\documentclass[overlapped,line,11pt]{res}
\usepackage{enumitem}
\usepackage{soul}

\oddsidemargin 0in
\evensidemargin 0in
\textwidth=6.25in
\topmargin=-0in
\textheight=8.75in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}
\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\name{Lawrence A. David \vspace*{.1in}}

\begin{resume}
\section{\underline{\sc Contact Information}}
\vspace{.05in}
\begin{tabular}{@{}p{4in}p{4in}}

CIEMAS, Room 2171     & {\it E-mail:}    l.d@duke.edu \\                
101 Science Drive, Box 3382   & {\it Phone:} 919.668.5388 \\
Durham, NC 27708 & {\it Web:} \url{http://www.ladlab.org} 

\end{tabular}

\section{\underline{\sc Education}}
\vspace{.05in}
Massachusetts Institute of Technology
\hfill 2005-2010\\

\vspace*{-5mm}
\begin{list1}
\item[] Ph.D., Computational \& Systems Biology
\item[] Thesis: Novel Phylogenetic Approaches to Problems in Microbial Genomics
\end{list1}

\vspace*{-2.5mm}
Columbia University \hfill 2001-2005\\
\vspace*{-5mm}
\begin{list1}
\item[] B.S., Biomedical Engineering, \emph{summa cum laude}
\end{list1}

\section{\underline{\sc Professional Experience}}
\vspace{.05in}
Associate Director, Duke Microbiome Center, Duke
University \hfill 2017-\hspace{7.5mm} \\
Assistant Professor, Biomedical Engineering, Duke
University \hfill 2016-\hspace{7.5mm} \\
Assistant Professor, Center for Genomic \& Computational Biology, Duke
University \hfill 2014-\hspace{7.5mm} \\
Assistant Professor,  Molecular Genetics \& Microbiology, Duke
University \hfill 2013-\hspace{7.5mm} \\
Junior Fellow \& PI, Harvard Society of Fellows - \emph{Mentor}: Dr. Peter Turnbaugh \hfill 2010-2013\\
Ph.D. student, Massachusetts Institute of Technology - \emph{Mentor}: Prof. Eric Alm \hfill
2005-2010 \\
Undergraduate researcher, Columbia University - \emph{Mentor}: Prof. Chris Wiggins
\hfill 2002-2005 

\section{\underline{\sc Fellowships \& Awards}} 
\vspace{.25in}

\begin{itemize}[leftmargin=1cm, style=sameline, itemsep=0mm]
\item[2018] Damon Runyon-Rachleff Innovator (1 of 6 nationwide)
\item[2018] Early-Career Systems Microbiologist, \emph{mSystems}
\item[2016] SN10: ScienceNews 10 Scientists to Watch
\item[2015] Beckman Young Investigator (1 of 8 nationwide)
\item[2015] Searle Scholar (1 of 15 nationwide)
\item[2015] Hartwell Investigator (1 of 12 nationwide)
\item[2014] Travel Grant, Duke-NUS Graduate Medical School
\item[2014] Alfred P. Sloan Research Fellow (1 of 12 biologists nationwide)
\item[2013] Whitehead Scholar, Duke University% (\$50K)
\item[2010] Elected Junior Fellow, Harvard Society of Fellows% (\$180K)
\item[2009] MIT Whitaker Health Sciences Fund Fellowship %(\$30K)
\item[2005] National Defense Science and Engineering Graduate
  Fellowship
\item[2005] Dept. of Energy Computational Science Graduate Fellowship [declined]
\item[2005] Ford Foundation Diversity Predoctoral Fellowship [declined]
\item[2005] Thomas ``Pop'' Harrington Award, Columbia University
\item[2005] Robert E. and Claire S. Reiss Graduate Prize, Columbia University
\item[2004] Elected, Tau Beta Pi
\item[2004] Barry M. Goldwater Scholarship
\item[2002] Westchester Filipino-American Scholarship
\item[2001] Columbia C.P. Davis Scholar

\end{itemize}

\section{\underline{\sc Publications}} 
\vspace{.1in} $[\ast$ denotes co-first authorship; \^{} denotes co-senior
  authorship; and, current/former David Lab members are \underline{underlined}$]$
\vspace{.1in}

\begin{revnumerate}[29]

\item{\ul{AT Reese}*, T Kartzinel*, \ul{B Petrone}, PJ Turnbaugh, R
  Pringle\^{}, \textbf{LA David}\^{}. Using DNA metabarcoding to
  evaluate the plant component of human diets: a proof of
  concept. \emph{Accepted}, \emph{\ul{mSystems}}, Sep 2019.}

\item{\ul{MM Villa}*, \ul{RJ Bloom}*, \ul{JD Silverman},
  \ul{HK Durand}, \ul{S Jiang}, \ul{A Wu}, S Huang, L You, \textbf{LA
    David}. High-throughput isolation and culture of human gut
  bacteria with droplet microfluidics. \emph{\ul{bioRxiv}},
  doi.org/10.1101/630822, May 2019.}

\item{\ul{JD Silverman}, \ul{RJ Bloom}, \ul{S Jiang}, \ul{HK Durand},
  S Mukherjee, \textbf{LA David}. Measuring and Mitigating PCR Bias in
  Microbiome Data. \emph{\ul{bioRxiv}}, doi.org/10.1101/604025, Apr 2019.}

\item{\ul{A Washburne}, \ul{J Silverman}, J Morton, D Becker, D
  Crowley, S Mukherjee, \textbf{LA David}, R Plowright. Phylofactorization - a
  graph partitioning algorithm to identify phylogenetic scales of
  ecological data. \emph{\ul{Ecological Monographs}}, 89(2):e01353, May 2019.}

\item{\ul{JD Silverman}, K Roche, S Mukherjee\^{}, \textbf{LA
      David}\^{}. Naught all zeros in sequence count data are the
    same. \emph{\ul{bioRxiv}}}, doi: https://doi.org/10.1101/477794, Nov 2018.

  \item {\ul{JD Silverman}, \ul{HK Durand}, \ul{RJ Bloom}, S
    Mukherjee, \textbf{LA David}. Dynamic linear models guide design
    and analysis of microbiota studies within artificial human
    guts. \emph{\ul{Microbiome}}, 6:202, Nov 2018.}

\item{\ul{JD Silverman}, L Shenhav, EA Halperin, SA Mukherjee\^{},
  \textbf{LA David}\^{}. Statistical Considerations in the Design
  and Analysis of Longitudinal Microbiome
  Studies. \emph{\ul{bioRxiv}}}, doi: https://doi.org/10.1101/448332,
  Oct 2018.

  \item {\ul{AT Reese}, FC Pereira, A Schintlmeister, D Berry, M
    Wagner, LP Hale, \ul{A Wu}, \ul{S Jiang}, \ul{HK Durand}, X Zhou,
    R Premont, AM Diehl, TM O’Connell, SC Alberts, TR Kartzinel, RM
    Pringle, RR Dunn, JP Wright, \textbf{LA David}. Microbial nitrogen
    limitation in the mammalian large intestine. \emph{\ul{Nature
        Microbiology}}, 3(12):1441-1450, Oct 2018.}

\item {\ul{AT Reese}, EH Cho, B Klitzman, SP Nichols, NA Wisniewski,
  \ul{MM Villa}, \ul{HK Durand}, \ul{FS Midani}, \ul{SN Nimmagadda},
  TM O’Connell, JP Wright, MA Deshusses, \textbf{LA
    David}. Antibiotic-induced changes in microbial respiration
  disrupt redox dynamics in the mouse gut. \emph{\ul{eLife}},
  7:e35987, Jun 2018.  }

\item {\ul{FS Midani}*, AA Weil*, F Chowdhury, YA Begum, AI Khan, MD
  Debela, \ul{HK Durand}, \ul{AT Reese}, \ul{SN Nimmagadda}, \ul{JD
    Silverman}, CN Ellis, ET Ryan, SB Calderwood, JB Harris, F Qadri,
  \textbf{LA David}\^{}, RC LaRocque\^{}. Human Gut Microbiota
  Predicts Susceptibility to \emph{Vibrio cholerae}
  Infection. \emph{\ul{Journal of Infectious Diseases}}, jiy192, Apr
  2018.}

\item {\textbf{LA David}. Towards personalized control of human gut
  bacterial communities. \emph{\ul{mSystems}},
  \textbf{3}(2) e00165-17, Mar 2018.}

\item {\underline{AT Reese}, K Lulow, \textbf{LA David}, JP
  Wright. Plant community and soil conditions individually affect soil
  microbial community assembly in experimental
  mesocosms. \emph{\ul{Ecology \& Evolution}}, \textbf{8}:1196-1205,
  Jan 2018.}

\item {\underline{JD Silverman}, \underline{A Washburne}, S Mukherjee, \textbf{LA David}. A
  phylogenetic transform enhances analysis of compositional microbiota
  data. \emph{\underline{eLife}}, 10.7554/eLife.21887, Feb 2017.}

\item {\underline{AD Washburne}, \underline{J Silverman}, JW Leff, DJ
  Bennett, J Darcy, S Mukherjee, N Fierer, \textbf{LA
    David}. Phylogenetic factorization of microbiome data yields
  lineage-level associations in microbiome
  datasets. \emph{\underline{PeerJ}}, \textbf{5}:e2969, Feb 2017.}

\item {Y Zhang, Y Zhao, \textbf{L David}, R Henao, L Carin. Dynamic
  Poisson Factor Analysis. \emph{\ul{IEEE 16th International
      Conference on Data Mining}}, 10.1109/ICDM.2016.0186, Dec 2016.}

\item {J Boursier, O Mueller, M Barret, M Machado, L Fizanne, F
  Araujo-Perez, C Guy, P Seed, J Rawls, \textbf{LA David}, G Hunault, F
  Oberti, P Cales, AM Diehl. The severity of NAFLD is associated with
  gut dysbiosis and shift in the metabolic function of the gut
  microbiota. \emph{\underline{Hepatology}}, \textbf{63}(3):764-775, Mar 2016.}

\item {S Wong, WZ Stephens, AR Burns, K Stagaman, \textbf{LA David},
  BJM Bohannan, K Guillemin, JF Rawls.  Ontogenetic Differences in
  Dietary Fat Influence Microbiota Assembly in the Zebrafish Gut.
  \emph{\underline{mBio}}, \textbf{6}(5):e00687-15, Sept 2015.}

\item {\textbf{LA David}, A Weil, ET Ryan, SB Calderwood, JB Harris, F
  Chowdhury, Y Begum, F Qadri, RC LaRocque, PJ Turnbaugh.  Gut
  microbial succession follows acute secretory diarrhea in humans.
 \emph{\underline{mBio}}, \textbf{6}(3):e00381-15, May 2015.}

\item {\textbf{LA David}, AC Materna, J Friedman, I Baptista, MC
  Blackburn, A Perrotta, SE Erdman, EJ Alm.  Host lifestyle affects
  human microbiota on daily timescales.
  \emph{\underline{Genome Biol}}, \textbf{15}:R89, Jul 2014.}

\item {\textbf{LA David}, CF Maurice, RN Carmody, DB Gootenberg, JE
  Button, BE Wolfe, AV Ling, AS Devlin, Y Varma, MA Fischbach, SB
  Biddinger, RJ Dutton, PJ Turnbaugh.  Diet rapidly and reproducibly
  alters the gut microbiome. \emph{\underline{Nature}},
  \textbf{505}(7484):559-563, Jan 2014.}

\item {G Szabo, SP Preheim, KM Kauffman, \textbf{LA David}, J Shapiro,
  EJ Alm, MF Polz.  Reproducibility of \emph{Vibrionaceae} Population
  Structure in Coastal Bacterioplankton. \emph{\underline{ISME J}},
  \textbf{7}:509-519, Mar 2013.}

\item {CS Smillie*, MB Smith*, J Friedman, OX Cordero, \textbf{LA
    David}, EJ Alm.  Ecology drives a global network of gene exchange
  connecting the human microbiome. \emph{\underline{Nature}},
  \textbf{480}(7376):241-244, Dec 2011.}

\item {\textbf{LA David}, EJ Alm.  Rapid evolutionary innovation during
  an Archean Genetic Expansion.  \emph{\underline{Nature}},
  \textbf{469}(7328):93-96, Jan 2011.}

\vspace*{1mm}
\item {SP Preheim, Y Boucher, H Wildschutte, \textbf{LA David},
  D Veneziano, EJ Alm and MF Polz.  Metapopulation
  structure of Vibrionaceae among coastal marine
  invertebrates. \emph{\underline{Environ Microbiol}}, \textbf{13}:265-275, Jan 2011.} 

\vspace*{1mm}
\item {BJ Shapiro, \textbf{LA David}, J Friedman, EJ Alm. Looking for
Darwin's footprints in the microbial world.  \emph{\underline{Trends Microbiol}}
\textbf{17}(5):196-204, May 2009.}

\vspace*{1mm}
\item { BJ Dubin-Thaler, JM Hofman, Y Cai, H Xenias, I Spielman, AV
  Shneidman, \textbf{LA David}, HG Dobereiner, CH Wiggins, MP Sheetz.
  Quantification of Cell Edge Velocities and Traction Forces Reveals
  Distinct Motility Modules during Cell Spreading. \emph{\underline{PLoS ONE}},
  \textbf{3}(11), Nov 2008.}

\vspace*{1mm}
\item {DE Hunt*, \textbf{LA David}*, D Gevers, SP Preheim, EJ Alm, MF
Polz.  Resource Partitioning and Sympatric Differentiation Among
Closely Related Bacterioplankton.  \emph{\underline{Science}},
\textbf{320}(5879):1081-85, May 2008.}

\vspace*{1mm}
\item {\textbf{LA David}, CH Wiggins. Benchmarking of dynamic Bayesian
  Networks from stochastic time-series data. \emph{\underline{Ann NY Acad Sci.}},
  \textbf{1115} 90-101, Dec 2007.}

\vspace*{1mm}
\item {CF Glenn, DK Chow, \textbf{L David}, C Cooke, M Gami, W Iser, K
  Hanselman, I Goldberg and CA Wolkow. Behavioral deficits during
  early states of aging in {\em Caenorhabditis elegans} result from
  locomotory deficits possibly linked to muscle frailty. \emph{\underline{J
    Gerontol A Biol Sci Med Sci.}}, \textbf{59}(12):1251-60, Dec 2004.}
\end{revnumerate}

\section{\underline{\sc Funded Research}} 
\vspace{.1in}
\emph{External Support}
\vspace{.1in}

\begin{itemize}[leftmargin=2cm, style=sameline]

\item[2019-2021] North Carolina Biotechnology Center, Translational
  Research Grant
  \newline Principal Investigator

\item[2018-2021] Office of Naval Research, N00014-18-1-2616
  \newline Principal Investigator

\item[2017-2019] Damon Runyon-Rachleff Innovation Award 
  \newline Co-Principal Investigator (with Co-PI:
  Anthony Sung)

\item[2017-2019] NASA NNX16A069A/T0106 \newline Principal Investigator


\item[2017-2022] NIH 1R01DK116187-01 \newline
  Principal Investigator

\item[2017-2018] CGIBD Pilot and Feasibility Award \newline Principal
  Investigator


\item[2016-2021] NIH 1R24-DK110492-01  \newline
  Co-Investigator (MPI: Rawls \& Seed)

\item[2016-2018] NIH 1R21-DK110496-01 \newline Co-Investigator (PI: Valdivia)

\item[2015-2019] Beckman Young Investigator Program
   \newline Principal Investigator

\item[2015-2018] Searle Scholars Program  \newline Principal Investigator 
  
\item[2015-2018] Hartwell Foundation, Individual Biomedical Research Award \newline Principal Investigator 


\item[2015-2017] National Science Foundation DDIG, DEB-1501495 \newline Principal Investigator (Co-PIs: Aspen Reese, Justin Wright) 


\item[2014-2016] Alfred P. Sloan Foundation, Research Fellowship \newline Principal Investigator 

\item[2014-2015] Global Probiotics Council, Young Investigator Grant  \newline Principal Investigator 

\end{itemize}

\emph{Internal Support}
\vspace{.1in}

\begin{itemize}[leftmargin=2cm, style=sameline]

\item[2018-2019] TriCEM-CHDI Pilot Research Grant
  \newline Co-Principal Investigator (with Co-PIs Sarah Armstrong \& Herman Pontzer) 

\item[2016-2017] Provost's Intellectual Community Planning Grant
  \newline Co-Principal Investigator (Organizer of 10
  Co-PIs) 

\item[2016-2017]  Collaborative Quantitative Approaches to Problems in Basic and Clinical Sciences, Pilot Grant
  \newline Co-Principal Investigator (with Co-PI:
  Sayan Mukherjee) 

\item[2015-2016] Duke Center for Genomic \& Computational Biology, Pilot Grant
  \newline Co-Principal Investigator (with Co-PI:
  Lingchong You)

\item[2013-2014] Duke Center for the Genomics of Microbial Systems
  \newline Co-Principal Investigator (with Co-PI:
  Marc Deshusses)

\item[2011-2012] Harvard University, Milton Fund \newline
  Principal Investigator

\item[2011-2012] Harvard Center for AIDS Reasearch, Feasibility Grant \newline
  Co-Principal Investigator (with Co-PI: Douglas Kwon)

\end{itemize}

\section{\underline{\sc Media}} 
\vspace{.05in} Print and online media coverage of research includes:
the BBC, Bloomberg, Boston Globe, the Daily Mail, GenomeWeb,
HealthDay, LiveScience, MSNBC, National Geographic: Phenomena, the New
Scientist, NPR, Prevention Magazine, Radio In Vivo (WCOM), Science
Daily, Science Friday, Science News, The Scientist, Scientific
American, StoryCollider, USA Today, and Wired.

\section{\underline{\sc Intellectual Property}} 
\vspace{.25in} 
\begin{revnumerate}[2]

\item {US Patent App. 16/323,203: Compositions and methods for
  measuring bacterial growth. L David, R Bloom, 2019.}
\item {US Patent App. 16/271,564: Rapid phenotyping and identification of microbes from a complex microbial community. M Villa, L David, R
  Bloom, 2019.}
\end{revnumerate}


\section{\underline{\sc Service}}
\vspace{.1in}

\emph{Editorial Service}
\vspace{.15in}

\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]
\item[2019-] Editor: \emph{mSystems}
\item[2017-2018] Editorial Board: \emph{Genome Magazine}
\item[2010-] Reviewer: \emph{Bioinformatics}, \emph{Biology Letters},
  \emph{BMC Bioinformatics}, \emph{BMC Microbiology},
  \emph{Biotechnology \& Bioengineering}, \emph{British Journal of
    Nutrition}, \emph{Canada Research Chair}, \emph{Cell Host \&
    Microbe}, \emph{Cell Reports}, \emph{Clinical Infectious
    Diseases}, \emph{eLife}, \emph{Environmental Microbiology},
  \emph{Genome Biology}, \emph{Genome Research}, \emph{Gut Microbes},
  \emph{InnoCentive}, \emph{ISMEJ}, \emph{J Biomed Informatics},
  \emph{J Clinical Investigation}, \emph{mBio}, \emph{Microbiome},
  \emph{National Science Foundation}, \emph{Nature Microbiology},
  \emph{npj Biofilms and Microbiomes}, \emph{PLoS Computational
    Biology}, \emph{PLoS One}, \emph{PLoS Pathogens}, \emph{PNAS},
  \emph{Science Translational Medicine}, \emph{Scientific Reports},
  \emph{Trends in Microbiology}.
\end{itemize}

\emph{International Service}
\vspace{.15in}

\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]
\item[2014] Instructor, ideSHi Genomics Workshop, International Centre for Diarrhoeal Disease Research, Dhaka, Bangladesh
\end{itemize}

\emph{National Service}
\vspace{.15in}

\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]
\item[2019] \emph{Ad hoc} reviewer, NCCIH/NIH review panel
\item[2019] Co-organizer, National Microbiome Centers Meeting
\item[2017] \emph{Ad hoc} reviewer, NIH Modeling \& Analysis of
  Biological Systems study section
\item[2016] Panel member, Discussion on Interdisciplinary Training,
  Burroughs Wellcome Fund
\item[2011-2013] Founding member, Junior Advisory Group, ASM General
  Meeting

\end{itemize}

\emph{Regional Service}
\vspace{.15in}


\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]
\item[2016-2019] Founding Member: NCBiotech Microbiome Consortium
\end{itemize}

\emph{University Service}
\vspace{.15in}


\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]
\item[2019] Co-organizer, Food Symposium
\item[2017-2018] Co-chair, Provost's Science Initiative, Genomics Subgroup
\item[2017] Co-organizer, Duke Integrative Bioinformatics for
  Investigating and Engineering Microbiomes Symposium
\item[2014] Co-organizer, Genomics of Microbial Systems Symposium
\end{itemize}

\emph{Departmental Service}
\vspace{.15in}
\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]
\item[2018-] Chair, MGM Diversity \& Inclusion Committee
\item[2016-2017] Member, admissions committee, CBB PhD program
\item[2016] Faculty liason, CBB seminar series
\item[2015-2017] Co-organizer, MGM departmental retreat
\item[2015-2016] Member, admissions committee, UPGG PhD program
\item[2014-2015] Member, amissions committee, MGM PhD program
\item[2013-2014] Member, admissions committee, CBB PhD program
\end{itemize}


\section{\underline{\sc Mentorship}}
\vspace{.1in}

\emph{Post-doctoral Associates}
\vspace{.1in}

\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]

\item[2015-] Dr. Max Villa \newline 
  PhD, Materials Science \& Engineering \newline
  Burroughs Wellcome Fund Postdoctoral Enrichment Program (2016) \newline
  Rising Stars in Biomedical Applications (2018)
\item[2016-2017] Dr. Alex Washburne \newline 
  PhD, Ecology \& Evolutionary Biology \newline
  Postdoctoral Fellow, Plowright Lab, Montana State University (2017-)
  
\end{itemize}

\vspace{-.1in}
\emph{Doctoral Students}
\vspace{.1in}

\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]

\item[2018-] Jeffrey Letourneau \newline 
  PhD Student, Molecular Genetics \& Microbiology \newline
  NSF Graduate Research Fellowship (2019)
\item[2018-] Brianna Petrone \newline 
  MD/PhD Student
\item[2017-] Zachary Holmes \newline 
  PhD Student, Molecular Genetics \& Microbiology \newline
  Department of Defense NDSEG Fellowship (2017) \newline
  NSF Graduate Research Fellowship (2017, declined)
\item[2015-2019] Justin Silverman \newline 
  MD/PhD Student, Computational Biology \& Bioinformatics \newline
  Assistant Professor, Pennsylvania State University (2020-)
\item[2014-2019] Rachael Bloom \newline 
  PhD Student, University Program in Genetics \& Genomics \newline
  UPGG Marcy Speer Fellowship (2014) \newline
  NSF Graduate Research Fellowship (2014) \newline
  Scientist, Resilient Biotics (2019-)
\item[2013-2018] Firas Midani \newline 
  PhD Student, Computational Biology \& Bioinformatics \newline
  Postdoctoral Fellow, Britton Lab, Baylor College of Medicine (2018-)
\item[2013-2017] Aspen Reese \newline 
  PhD Student, University Program in Ecology \newline
  NSF Graduate Research Fellowship (2014) \newline
  Department of Defense NDSEG Fellowship (2014, declined) \newline
  NSF Doctoral Dissertation Improvement Grant (2015) \newline
  PI \& Junior Fellow, Harvard Society of Fellows (2017-2020) 
  %Assistant Professor, University of San Diego (2020-) 
\end{itemize}

\vspace{-.1in}
\emph{Medical Students}
\vspace{.1in}
\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]

\item[2018-] Diana Dayal (University of North Carolina, Chapel Hill)
\end{itemize}

\vspace{-.1in}

\emph{Undergraduate Students}
\vspace{.1in}
\begin{itemize}[leftmargin=2cm, style=sameline, itemsep=0mm]

\item[2019-] Mohsin Haider, Mechanical Engineering
\item[2018-] Savita Gupta, Neuroscience \& English
\item[2017-] Miranda Metz, Biology \& Global Health 
\item[2018-2019] Sam Kim, Biology \& Computer Science
\item[2015-2018] Andrew Grover, Biochemistry 
\item[2015-2017] Lionel Watkins, Biomedical Engineering 
\item[2014-2017] Anchi Wu, Biomedical Engineering \newline 
  Duke Helmholtz Prize for best UG research project in BME (2017) \newline
  Duke Pratt Fellow (2015-2016) \newline
  GCB Summer Research Fellowship (2015) 
\item[2013-2017] Sai Nimmagadda, Biomedical Engineering \newline
  IGSP Summer Research Fellowship (2014) \newline
  SMIF Undergraduate User Program (2014)
\item[2015-2016] Vivek Sriram, Computer Science
\item[2013-2015] Eric Mastrolonardo, 
  Biology 
\item[2013-2014] Calvin Lau, Biology 
\item[2013-2014] Olivia Lin, Biology
\item[2012] Noah Apthorpe (\emph{at Harvard, supervised by Peter Turnbaugh})
\item[2010] Shirley Galbiati (\emph{at MIT, supervised by Eric Alm})
p\item[2008-2010] Albert Wang (\emph{at MIT, supervised by Eric Alm})
\item[2008] Alexandra Konings (\emph{at MIT, supervised by Eric Alm})
\item[2008-2010] MacGregor F Entry (\emph{at MIT, Graduate Resident Tutor})
\end{itemize}

\section{\underline{\sc Invited Presentations}}
\vspace{.25in}

\begin{revnumerate}[69]

\item {Anaerobe Congress, Seattle, WA, Jul 2020 }

\item {ASM Microbe 2020, Chicago, IL, Jun 2020 }

\item {International Conference on Microbiome Engineering, Boston, MA, Dec 2019 }

\item {Department of Defense Tri-Service Microbiome Consortium 3rd
  Annual Meeting, Wright Patterson Air Force Base, Fairborn, OH, Oct
  2019 }

\item {Grand Rounds, Division of Endocrinology, Duke University School of
  Medicine, Durham, NC, Aug 2019
  }

\item {Cornell EvoDay (Harrison Keynote Lecture), Ithaca, NY, May 2019}

\item {Special Seminar, Molecular Biology \& Biochemistry, UC Irvine, Irvine, CA, Apr 2019}

\item {ASBMB Annual Meeting, Orlando, FL, Apr 2019}

\item {Precision Medicine World Conference, Duke University, Durham, NC, Sep 2018}

\item {Pharmaceutical Sciences Conference, UNC Chapel Hill, Chapel Hill, NC, Jun 2018}

\item {CGIBD Seminar Series, UNC Chapel Hill, Chapel Hill, NC, Apr 2018}

\item {Seminar Series, AgBiome, Research Triangle Park, NC, Dec 2017}

\item {11th International Conference in Bioinformatics, Georgia Tech, Atlanta, GA, Nov 2017}

\item {Bioinformatics for the Microbiome Symposium, Stanford University, Palo Alto, CA, Sep 2017}

\item {Molecular Pathogenesis \& Host Response Meeting, Cold Spring Harbor Laboratory, Cold Spring, NY, Sep 2017}

\item {Ecological Society of America Annual Meeting, Portland, OR, Aug 2017}

\item {Pharmaceutical Sciences Conference, UNC Chapel Hill, Chapel Hill, NC, May 2017}

\item {Precision Medicine World Conference, Duke University, Durham, NC, May 2017}

\item {Inflammation, Immunity, and Infectious Diseases Seminar, University of Utah, Salt Lake City, UT, May 2017}

\item {Microbiology Seminar, NC State University, Raleigh, NC, Mar 2017}

\item {RTP 180: Microbiomes, Raleigh, NC, Jan 2017}

\item {Triangle Microbial Interactions Seminar, Chapel Hill, NC, Dec 2016}

\item {Hartwell Foundation Symposium, Case Western University, Cleveland, OH, Sep 2016}

\item {Food-Microbiome Interaction: Implications for Human Health and Disease, Royal Society, London, UK, May 2016}

\item {BASF Plant Science, Research Triangle Park, NC May 2016}

\item {Bioinformatics and Genomics Seminar, UNC Charlotte, Charlotte, NC, Apr 2016}

\item {Microbiome Research in Progress Seminar, UNC Chapel Hill, Chapel Hill, NC, Mar 2016}

\item {First Workshop on Statistical and Algorithmic Challenges in Microbiome Data Analysis, New York, NY, Feb 2016}

\item {US Probiotics Scientific Board Meeting, New York, NY, Feb 2016}

\item {Department of Microbiology and Immunology Seminar, McGill University, Montreal, Canada, Dec 2015}

\item {Digestive Disease Lecture Series, University of Chicago, Chicago, IL, Nov 2015}

\item {Symposium on Biotechnology, University of Missouri, St. Louis, MO, Nov 2015}

\item {Hartwell Foundation Symposium, University of Wisconsin, Madison, WI, Sep 2015}

\item {HHMI Science Symposium, University of Richmond, Richmond, VA, Sep 2015 (Keynote)}

\item {Infectious Disease Seminar, NC State College of Veterinary Medicine, Raleigh, NC, Apr 2015}

\item {Duke-NUS Symposium, Duke-NUS Graduate Medical School, Singapore, Mar 2015}

\item {Alumni Association Board Meeting, Duke University,
  Durham, NC, Feb 2015
  }

\item {Biology of Populations Colloquium, Princeton University, Princeton, NJ, Dec 2014
  }

\item {Board of Trustees Meeting, Duke University,
  Durham, NC, Sep 2014
  }

\item { The Human and Environmental Microbiome Symposium, Duke University,
  Durham, NC, Sep 2014
  }

\item {The 20$^{th}$ International Microbial Genomes Conference, UCLA
  Conference Center, Lake Arrowhead, CA, Sep 2014
  }

\item {Grand Rounds, Department of Pediatrics, Duke University School of
  Medicine, Durham, NC, Sep 2014
  }

\item {Oral Biology Seminar Series, School of Dentistry, University of
  North Carolina, Chapel Hill, NC, Sep 2014
  }

\item {Grand Rounds, Department of Gastroenterology, Duke University School of
  Medicine, Durham, NC, Sep 2014
  }

\item {Bollum Symposium, University of Minnesota, Minneapolis, MN, May 2014
  }

\item {DCEG Fellows’ Training Symposium, NIH/NCI, Bethesda, MD, Mar 2014
  }

\item {LadHyX Seminar, Ecole
  Polytechnique, Palaiseau, France, Feb 2014}

\item {Pasteur Fellowship Visiting Scholar, Institut Pasteur,
  Paris, France, Feb 2014}

\item {Duke University Program in Ecology Seminar,
  Durham, NC, Nov 2013}

\item {Duke Marine Lab Fall Seminar,
  Beaufort, NC, Sep 2013}

\item {Duke Computational Biology \& Bioinformatics Seminar,
  Durham, NC, Sep 2013}

\item {Duke Genomic and Personalized Medicine Forum,
  Durham, NC, Sep 2013}

\item {Duke University Program in Genetics \& Genomics Seminar,
  Durham, NC, Sep 2013}

\item {Genomics Standards Consortium 15,
  Bethesda, MD, Apr 2013}

\item {Museum of Science, Boston,
  MA, Mar 2013}

\item {National Institute of Health, Manila,
  Philippines, Feb 2013}

\item {Civil \& Environmental Engineering Seminar, Duke University,
  Durham, NC, Dec 2012}

\item {icddr,b Seminar, Dhaka,
  Bangladesh, Aug 2012}

\item {International Research in
  Infectious Diseases Annual Meeting, Bethesda, MD, May 2012}

\item {MIT Synthetic Biology Lunch, Cambridge, MA, Apr 2012}

\item {Northeastern University, Boston, MA, Mar 2012}

\item {Memorial Sloan-Kettering Cancer Center, New York, NY,
  Feb 2012}

\item {Duke University, Durham, NC, Feb 2012}

\item {University of North Carolina, Chapel Hill, NC, Feb 2012}

\item {Microbiome Research
  in the Boston Area Seminar, Boston, MA, Oct 2011}

\item {Microbiome Seminar,
  New York University, New York, NY, Oct 2011}

\item {Paleobiology in the Genomics Era
  Conference, JCVI, San Diego, CA, May 2011}

\item {Quantitative Biology Workshop, MIT, Jan 2011}

\item {Ginkgo BioWorks, Boston, MA, Mar 2010}

\end{revnumerate}


%\section{\underline{\sc Patents}} 
%\vspace{.25in}
%\begin{list2}
%\item Diagnosis of Patient Health By Deep Multiplexed Environmental
%  16S Sequencing.  EJ Alm, LA David, S Levine, A Materna.
%  \emph{Application underway.}
%\end{list2}


\end{resume}
\end{document}




